Staged Abstract Interpreters

### 2019-09-09 paper/50_stageabs.tex
misc

\begin{itemize}
  \item Constructing a generic interpreter that abstracts over binding times,
    value domains, and primitive operations. In this paper, the generic interpreter
    is implemented in monadic style; therefore, the semantics can be encapsulated
    into monads.
  \item Then we can implement an unstaged abstract interpreter modularly using
    the appropriate monad stack. This step has been explored in the previous
    literatures.
  \item Finally, we replace the monad stack with a staged monad stack, and
    refactor related primitive operations.  Such staged monads operate on
    staged data types, i.e., next-stage values.
\end{itemize}

>>>>

\begin{itemize}
  \item First, we construct a generic interpreter that abstracts over binding times,
    value domains, and primitive operations. In this paper, the generic interpreter
    is implemented in monadic style; therefore, the semantics can be encapsulated
    into monads.
  \item Then, we implement an unstaged abstract interpreter modularly using the
    appropriate monad stack. This step has been explored in the previous
    literatures.
  \item Finally, we replace the monad stack with a staged monad stack, and
    refactor related primitive operations.  Such staged monads operate on
    staged data types, i.e., next-stage values.
\end{itemize}
